Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-07-12 article-models-ttinternal.tex
small changes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Projection algebras}
Projection algebras will be weakening algebras with additional terms implementing
the identity terms. We call these algebras projection algebras because the
identity terms can only be formulated in weakening algebras and together with
weakening, the identity terms provide for all the projections. In a weakening
algebra $\cftalg{A}$ in context $\Gamma$, identity terms are implemented by a term
\begin{equation*}
\jterm
  { { {\Gamma}
      {\cftalgc{\cftalg{A}}}
      }
    { \cftalgf{\cftalg{A}}
      }
    }
  {\subst{{\idtm{\cftalgf{\cftalg{A}}}}{\cftwkc{\cftalg{A}}}}{\cftalgt{\cftfamalg{\cftalg{A}}}}}
  {\cftidtm{\cftalg{A}}}
\end{equation*}
We will require additionally that identity terms are compatible with weakening.
Thus we will formulate an abstraction of the rule stated in \autoref{comp-wi}.

\begin{equation}
\jtermeq
  { \xi}
  { \xi}
  { \subst
      { \jcomp
          { }
          { \cftctxext}
          { \cftidtm{\cftalg{A}}
            }
        }
      { { { \idtm
              { \jcomp
                  { }
                  { \cftctxext}
                  { \cftalgf{\cftalg{A}}
                    }
                }
            }
            { \jcomp
                { }
                { \cftctxext
                  }
                { \cftwkc{\cftalg{A}}
                  }
              }
          }
        { \jcomp
            { }
            { \jcomp{}{\cftctxext}{\cftfamext}}
            { \cftwkt{\cftalg{A}}}
          }
        }
    }
  { \xi}
\end{equation}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{E-algebras}
E-algebras will be CFT-algebras with a weakening operation, identity terms and
a substitution operation making it a projection algebra and a substitution 
algebra at the same time. Additionally the weakening operation, identity terms
and the substitution operation are all required to be compatible with each
other. Thus, we need to require the abstractions of the rules stated in
\autoref{comp-sw,comp-ws,cancellation-ws,cancellation-i}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Projection algebras}
Projection algebras will be weakening algebras with additional terms implementing
the identity terms. We call these algebras projection algebras because the
identity terms can only be formulated in weakening algebras and together with
weakening, the identity terms provide for all the projections. In a weakening
algebra $\cftalg{A}$ in context $\Gamma$, identity terms are implemented by a term
\begin{equation*}
\jterm
  { { {\Gamma}
      {\cftalgc{\cftalg{A}}}
      }
    { \cftalgf{\cftalg{A}}
      }
    }
  {\subst{{\idtm{\cftalgf{\cftalg{A}}}}{\cftwkc{\cftalg{A}}}}{\cftalgt{\cftfamalg{\cftalg{A}}}}}
  {\cftidtm{\cftalg{A}}}
\end{equation*}
We will require additionally that identity terms are compatible with weakening,
i.e.~an abstraction of the rule stated in \autoref{comp-wi}. Since this is the
only additional rule for projection algebras, we immediately state the 
definition.

\begin{defn}
A \emph{projection algebra $\cftalg{A}$ in context $\Gamma$} is a weakening algebra
$\cftalg{A}$ in context $\Gamma$ together with a term
\begin{equation*}
\jterm
  { { {\Gamma}
      {\cftalgc{\cftalg{A}}}
      }
    { \cftalgf{\cftalg{A}}
      }
    }
  {\subst{{\idtm{\cftalgf{\cftalg{A}}}}{\cftwkc{\cftalg{A}}}}{\cftalgt{\cftfamalg{\cftalg{A}}}}}
  {\cftidtm{\cftalg{A}}}
\end{equation*}
satisfying the judgmental equality
\begin{align*}
& \subst
  { \ctxwk
      { \cftalgf{\cftalg{A}}}
      { \jcomp
        { }
        { \cftctxext}
        { \cftidtm{\cftalg{A}}
          }
        }
    }
  { { \ctxwk
        { \cftalgf{\cftalg{A}}}
        { \subst { \idtm
            { \jcomp
                { }
                { \cftctxext}
                { \cftalgf{\cftalg{A}}
                  }
              }
          }
          { \jcomp
              { }
              { \cftctxext
                }
              { \cftwkc{\cftalg{A}}
                }
            }
          }
      }
    { \jcomp
        { }
        { \ctxwk{\cftalgf{\cftalg{A}}}{\cftfamext}}
        { \cftwkt{\cftalg{A}}}
      }
    }
  \\
& \jdeq
  \jcomp{}
    { \cftwkf{\cftalg{A}}}
    { \jcomp{}
        { \cftwkc{\cftalg{A}}}
        { \jcomp{}
            { \cftctxext}
            { \jcomp{}
              { \cftctxext}
              { \cftidtm{\cftalg{A}}}
              }
          }
      }
\end{align*}
of terms of %
$ \jcomp{}
    { \cftwkf{\cftalg{A}}}
    { \jcomp{}
        { \cftwkc{\cftalg{A}}}
        { \jcomp{}
            { \cftctxext}
            { \jcomp{}
              { \cftctxext}
              { \subst
                  { {\idtm{\cftalgf{\cftalg{A}}}}
                    {\cftwkc{\cftalg{A}}}
                    }
                  { \cftalgt{\cftfamalg{\cftalg{A}}}
                    }
                }
              }
          }
      }$
in context \ldots.

The term $\cftidtm{\cftalg{A}}$ of a projection algebra $\cftalg{A}$ in context
$\Gamma$ is called the \emph{internal identity term of $\cftalg{A}$}.
\end{defn}

\begin{rmk}
We shall have to verify that the condition on the internal identity term 
$\cftidtm{\cftalg{A}}$ of a projection algebra $\cftalg{A}$ in context $\Gamma$
is indeed well-typed. More precisely, we have to demonstrate that the judgmental
equality
\begin{align*}
& \jdeq
  \jcomp{}
    { \cftwkf{\cftalg{A}}}
    { \jcomp{}
        { \cftwkc{\cftalg{A}}}
        { \jcomp{}
            { \cftctxext}
            { \jcomp{}
              { \cftctxext}
              { \subst
                  { {\idtm{\cftalgf{\cftalg{A}}}}
                    {\cftwkc{\cftalg{A}}}
                    }
                  { \cftalgt{\cftfamalg{\cftalg{A}}}
                    }
                }
              }
          }
      }  
\end{align*}
of families in context \ldots holds.
\end{rmk}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{E-algebras}
E-algebras will be CFT-algebras with a weakening operation, identity terms and
a substitution operation making it a projection algebra and a substitution 
algebra at the same time. Additionally the weakening operation, identity terms
and the substitution operation are all required to be compatible with each
other. Thus, we need to require the abstractions of the rules stated in
\autoref{comp-sw,comp-ws,cancellation-ws,comp-si,cancellation-i}.

\subsection{E-homomorphisms}
\begin{defn}
An \emph{E-homomorphism from $\cftalg{A}$ to $\cftalg{B}$ in context $\Gamma$}
is a CFT-homomorphism which is both a projection homomorphism and a
substitution homomorphism.
\end{defn}

\subsection{E-transformations}
E-transformations are going to be the analogues of natural transformations.

\subsection{E-adjunctions}
